### 2021-10-21 submission/response_to_reviewers.md

**Line 200: It's a little challenging to determine what happened here: "First, I sampled sequences from the null distribution for each dataset and randomly assigned each sample to one of two treatment groups and determined the richness and diversity of ASVs and OTUs". For example, what is meant by "sequences" here? ASVs? How did you sample the sequences? Are you saying that you subsampled the data somehow? I recommend you clarify.**

I have restructured the text here to make it more clear how the simulations were created.

@@

**Line 204: What is meant by "meaningfully vary"? Was this quantified in some manner?**

I have inserted the median, minimum, and maximum p-values that were observed across the range of conditions that are listed in these sentences.

@@

**Line 215: "However, when rare taxa of any frequency were removed, the probability of falsely detecing a difference as signifiant increased with the definition of rarity". But Fig 5B seems to show that the rate only tends to increase when singletons are removed, such that the rate is flat as more abundant rare sequences are removed.**

The reviewer is correct that the curve is flat; however, the curve flattens at a very high level when any rare sequences were removed. That's the problem. The value is the lowest when all sequences were retained. The reviewer has correctly identified the problem: if any sequences are removed, the false detection rate increases dramatically.

@@

**Line 236: "The practice of removing rare sequences from samples seems to be a response to researchers prioritizing the number of reads and length of sequences over their quality." I'm not sure this is entirely accurate. Some of it stems from this, but it also appears to have emerged as a way to control for overclustering, which often results in spurious OTUs. This methodology may have been a holdover in the era of ASV analysis, where it may not be as critical.**

This sentence has been modified to reflect that the perception of overclustering is a product of prioritizing the number of read depth and length of sequences. Again, we don't know what is too many OTUs if we don't know the true number of OTUs in natural samples

@@

**Line 250: "In practice, I suspect this range is actually larger since researchers may have opted against depositing samples with fewer reads into the SRA". Perhaps. But this would imply that such samples were not (nor would be) included in the analysis and not subject to the bias being discussed here.**

This sentence has been removed in the revised manuscript

**Line 255: I think I follow your intention, but note that your results of finding that rare sequences are higher in shallow depth samples seems initially at odds with the subsequent part of the discussion that observes that "number of spurious sequences increases with sequencing depth". You can avoid some confusion by using this observation is the expectation and then discussing how your results differ from this expectation, reinforcing the interpretation that the rare sequences observed in your analysis are real variants. This may be your intention in the current narrative; I simply recommend a modest restructure of this logic to improve comprehension.**

As suggested by the reviewer, this text has been revised to make it more clear.
